---
title: "YAML header"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{YAML header}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo = FALSE}
img {
  width: 85%;
  display: block;
  margin-left: auto;
  margin-right: auto;
  margin-top: 5px;
  margin-bottom: 5px;
}
.column2 {
  float: left;
  width: 49%;
  margin: 2px;;
}
.column3 {
  float: left;
  width: 33%;
}

/* Clear floats after the columns */
.row:after {
  content: "";
  display: table;
  clear: both;
}
.medium > p > img {
  width: 50%;
}
.small > p > img {
  width: 30%;
}
```


## reference_docx

The argument `reference_docx` (see `?rmarkdown::word_document`) lets you to use
styles and settings from a template which is a Word document (`*.docx`).

The `R Markdown` documentation on this topic is available via:  
<https://bookdown.org/yihui/rmarkdown/word-document.html>

Taking full advantage of the package's capabilities requires the use of document
templates in which various styles and formatting parameters are stored.

You can create or re-use a Microsoft Word document that will be used as template
(ex: “template.docx”); it will contain the lists definitions, the table styles,
the title and paragraph styles, default fonts and many other settings. 


### Usage

This template will be used as a reference document for the customization of your
list style with R Markdown. To use this feature, specify the `reference_docx`
option in `YAML`.

By default, your YAML header looks like this:  

`````
---
date: "`r Sys.Date()`"
author: "superman"
title: "Document title"
output: 
  officedown::rdocx_document
---
`````

::::: row

::: column2

Add `reference_docx` argument to the `YAML`: 

`````
---
date: "`r Sys.Date()`"
author: "superman"
title: "Document title"
output: 
  officedown::rdocx_document:
     reference_docx: template.docx
---
`````

:::

::: column2

When using `bookdown`, it should be:

`````
---
date: "`r Sys.Date()`"
author: "superman"
title: "Document title"
output: 
  bookdown::markdown_document:
    base_format: "officedown::rdocx_document"
    reference_docx: template.docx
---
`````


:::


:::::


## Settings and default values

There is a mechanism to overwrite the defaults with the specified values. This
makes it possible not to fill in all the arguments. Thus, a header like the
following one is valid:

```yaml
# officedown yaml header
output: 
  officedown::rdocx_document:
    tables:
      caption:
        pre: 'tab. '
```


## Default settings

The package is using global settings, used for customization of tables, lists,
plots and captions.

Default values are presented below in their YAML format.

```yaml
# full default yaml header
output: 
  officedown::rdocx_document:
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    plots:
      style: Normal
      align: center
      caption:
        style: Image Caption
        pre: 'Figure '
        sep: ': '
    lists:
      ol.style: null
      ul.style: null
```

Default values are detailled in the help page of `rdocx_document`, see details
with command:

```{r eval=FALSE}
?officedown::rdocx_document
```

