```{r, child = "./setup.Rmd", include = FALSE}
```

The parameter lists is a list that can contain two named items:

- `ol.style`: style to use for ordered lists.
- `ul.style`: style to use for unordered lists.

Default values are `list(ol.style = NULL, ul.style = NULL)`.

Expected values are the stylenames to be used to replace the style of ordered and unordered lists created by pandoc. If NULL, no replacement is made.

These values in YAML format are:

```markdown
output: 
  officedown::rdocx_document:
    lists:
      ol.style: null
      ul.style: null
```

They can have values corresponding to existing stylenames
(of type 'numbering'). With package 'officer', we can 
read these values with [styles_info()][officer::styles_info].

```{r}
library(officer)
docx_file <- system.file(
  package = "officedown", "examples",
  "bookdown", "template.docx"
)
doc <- read_docx(docx_file)
styles_info(doc, type = "numbering")[, 1:6]
```

From the above available values, the possible configuration
is possible:

```markdown
output: 
  officedown::rdocx_document:
    lists:
      ol.style: 'Default ol'
      ul.style: 'Default ul'
```
