---
author: 'Bruce'
date: '0189-12-27'
output: 
  officedown::rdocx_document:
      mapstyles:
        Normal: ['First Paragraph', 'Author', 'Date']
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(officedown)
library(officer)
fp <- fp_par(text.align = "center", padding.top = 120)
ft <- fp_text(font.size = 12, bold = TRUE, color = "#C32900", font.family = "Cambria")
```

## Chunk outputs

The package `r ftext("officedown", ft)` is great. 

This is a Word field, the file size is `r run_seqfield("FILESIZE \\k \\* MERGEFORMAT")` Kb. 

## Paragraph settings

This text is centered `r fp_par(text.align = "center")`.

## Section definitions

<!---BLOCK_MULTICOL_START--->

This text is on column 1. This text is on column 1.
This text is on column 1. This text is on column 1.
This text is on column 1. This text is on column 1.
This text is on column 1. This text is on column 1.
This text is on column 1. This text is on column 1.`r fp_par(text.align = "justify")`
`r run_columnbreak()`

This text is on column 2.
This text is on column 2.
This text is on column 2.
This text is on column 2.
This text is on column 2.
This text is on column 2.`r fp_par(text.align = "justify")`

<!---BLOCK_MULTICOL_STOP{widths: [3,3], space: 0.2, sep: true}--->


<!---BLOCK_LANDSCAPE_START--->

This is a landscape section.`r fp`

<!---BLOCK_LANDSCAPE_STOP--->


This is a custom section using `block_section`.`r fp`

```{r}
ps <- prop_section(
  page_margins = page_mar(bottom = 1, top = 2, left = 1.5),
  type = "oddPage"
)
block_section(ps)
```

We are back on default section.`r fp`
